An open reproducible framework for the study of the iterated prisoner's dilemma

### 2016-02-08 tex/paper.tex
Addressing minor comments from O and M.

\begin{figure}[!hbtp]
    \begin{minted}[breaklines, linenos, frame=lines]{python}
>>> import axelrod
>>> strategies = [s() for s in axelrod.demo_strategies]
>>> tournament = axelrod.Tournament(strategies)
>>> results = tournament.play()
>>> plot = axelrod.Plot(results)
>>> plot.boxplot()  # doctest:+SKIP
    \end{minted}
    \caption{A simple set of commands to create a demonstration tournament. The
        output is shown in Figure~\ref{fig:demo_tournament}.}
    \label{fig:demo_tournament_commands}
\end{figure}

@@

\begin{figure}[!hbtp]
    \begin{minted}[breaklines, linenos, frame=lines]{python}
class Grudger(Player):
    """A player starts by cooperating however will defect if
       at any point the opponent has defected."""

@@

\begin{figure}[!hbtp]
    \begin{minted}[breaklines, linenos, frame=lines]{python}
class TestGrudger(TestPlayer):

@@

Due to the open nature of the library the number of strategies included has
grown at a fast pace, as can be seen in
Figure~\ref{fig:number_of_strategies_against_date}. Despite this, due to
previous research being done in an irreproducible way due to, for example no
source code, and/or vaguely described strategies; not all previous tournaments
are yet to be reproduced.

@@

\begin{figure}[!hbtp]
    \begin{minted}[breaklines, linenos, frame=lines]{python}
>>> import axelrod

@@

Work is actively ongoing to include more strategies. In the next Section, an
overview of some of the early and novel research insights made possible by the
library.

@@

The above example is an incomplete illustration of the mapping for \(m=8, n=2\).
Intuitively this state space uses the initial plays of the opponent to gain some
information about the intentions of it whilst still taking in to account the
recent play.  The actual winning strategy an instance of the this framework for
\(m=n=2\) for which an evolutionary algorithm has been used to train it. More
details of this can be found in \cite{mojones}. In \cite{} experiments are
carried out to evaluate how this particular strategy behaves in environments
other than those in which it was trained\dots

@@

\begin{itemize}
    \item A closer look at zero determinant strategies, showing that
        extortionate strategies obtain a large number of wins \textit{but} do
        not perform particularly well. This is relevant given the findings of
        \cite{Stewart2012} in which zero determinant strategies are shown to be
        able to perform better than a given other strategy. This finding extends
        to noisy tournaments (which are also implemented in the library).
    \item This negative relationship between wins and performance does not
        generalise, there are some strategies that perform well, both in terms
        of matches won and overall performance: Back stabber, Double crosser and
        Fool Me Once. These strategies continue to perform well in noisy
        tournaments.
    \item Strategies like LookerUp and MetaHunter seem to be generally
        cooperative yet still exploit naive strategies. The MetaHunter strategy
        is a particular type of Meta strategy which uses a variety of other
        strategy behaviours to choose a best action. These strategies perform
        very well in general and continue to do so in noisy tournaments.
\end{itemize}

@@

This paper has presented a game theoretic software package that aims to address
reproducibility of research in to the iterated prisoner's dilemma. Through the
very nature of the development of this library, all open research and
development, it has not only acquired a large number of strategies (120) but
also already discovered various insights that will lead to further publications.

>>>>

\begin{figure}[!hbtp]
    \begin{minted}[linenos, frame=lines]{python}
>>> import axelrod
>>> strategies = [s() for s in axelrod.demo_strategies]
>>> tournament = axelrod.Tournament(strategies)
>>> results = tournament.play()
>>> plot = axelrod.Plot(results)
>>> plot.boxplot()  # doctest:+SKIP
    \end{minted}
    \caption{A simple set of commands to create a demonstration tournament. The
        output is shown in Figure~\ref{fig:demo_tournament}.}
    \label{fig:demo_tournament_commands}
\end{figure}

@@

\begin{figure}[!hbtp]
    \begin{minted}[linenos, frame=lines]{python}
class Grudger(Player):
    """A player starts by cooperating however will defect if
       at any point the opponent has defected."""

@@

\begin{figure}[!hbtp]
    \begin{minted}[linenos, frame=lines]{python}
class TestGrudger(TestPlayer):

@@

Due to the open nature of the library the number of strategies included has
grown at a fast pace, as can be seen in
Figure~\ref{fig:number_of_strategies_against_date}. Despite this, due to
previous research being done in an irreproducible, with for example no
source code, and/or vaguely described strategies, not all previous tournaments
are yet to be reproduced. In fact, some of the early tournaments might be
impossible to reproduce as the source code is forever lost, this library aims to
prevent this from happening again in the future.

@@

\begin{figure}[!hbtp]
    \begin{minted}[linenos, frame=lines]{python}
>>> import axelrod

@@

Work is ongoing to include more strategies. In the next Section, an
overview of some of the early and novel research insights made possible by the
library is described.

@@

The above example is an incomplete illustration of the mapping for \(m=8, n=2\).
Intuitively this state space uses the initial plays of the opponent to gain some
information about its intentions whilst still taking in to account the
recent play. The actual winning strategy is an instance of the framework for
\(m=n=2\) for which an evolutionary algorithm has been used to train it. More
details of this can be found in \cite{mojones}. In \cite{} experiments are
carried out to evaluate how this particular strategy behaves in environments
other than those in which it was trained\dots

@@

\begin{itemize}
    \item A closer look at zero determinant strategies, showing that
        extortionate strategies obtain a large number of wins \textit{but} do
        not perform particularly well. This is relevant given the findings of
        \cite{Stewart2012} in which zero determinant strategies are shown to be
        able to perform better than any other strategy. This finding extends
        to noisy tournaments (which are also implemented in the library).
    \item This negative relationship between wins and performance does not
        generalise. There are some strategies that perform well, both in terms
        of matches won and overall performance: Back stabber, Double crosser,
        Looker Up, and Fool Me Once. These strategies continue to perform well in noisy
        tournaments, however some of these have knowledge of the length of the
        game (Back stabber and Double crosser). This is not necessary to rank
        well in both wins and score as demonstrated by Looker Up and Fool Me
        Once.
    \item Strategies like LookerUp and MetaHunter seem to be generally
        cooperative yet still exploit naive strategies. The MetaHunter strategy
        is a particular type of Meta strategy which uses a variety of other
        strategy behaviours to choose a best action. These strategies perform
        very well in general and continue to do so in noisy tournaments.
\end{itemize}

@@

This paper has presented a game theoretic software package that aims to address
reproducibility of research into the iterated prisoner's dilemma. The open
nature of the development of the library has lead rapidly to the inclusion of
many well known strategies, many novel strategies, and new and recapitulated
insights.
